Reasoning about Connectors in Coq

### 2017-06-02 FACS_Extension/paper_revised0508.tex
the soundness theorem and the new example are added

\subsection{The Coordination Model Reo}
Reo is a channel-based exogenous coordination model wherein complex coordinators, called connectors,
are compositionally built out of simpler ones \cite{Arb04}.
Further details about Reo and its semantics can be found in \cite{Arb04,AR03,BSAR06}.
The simplest connectors are channels with well-defined behavior such as synchronous channels, FIFO channels, etc.
Each channel in Reo has exactly two directed ends, with their own identities.
There are two types of channel ends: source ends and sink ends. A source channel end accepts
data into the channel. A sink channel end dispenses data out of the channel.
\begin{figure}
  \centering
  \begin{tikzpicture}
  \draw (0.7, 0.6) node[draw=none] {Sync};
  \sync{(0,1)}{(1.5,1)}{}
  \draw (2.7, 0.6) node[draw=none] {Syncdrain};
  \syncdrain{(2,1)}{(3.5,1)}{node[below]{}}
  \draw (4.7, 0.6) node[draw=none] {FIFO1};
  \fifoe{(4,1)}{(5.5,1)}{node[below]{}}
  \draw (6.7, 0.6) node[draw=none] {Asyncdrain};
  \asyncdrain{(6,1)}{(7.5,1)}{node[below left]{}}
  \draw (8.7, 0.6) node[draw=none] {LossySync};
  \lossysync{(8,1)}{(9.5,1)}{node[below left]{}}
  \end{tikzpicture}\vspace{-6mm}
  \caption{Five types of basic channels.}\label{fig:basicchannel}
\end{figure}

@@

By means of function \emph{Conjunction}, basic channels are defined concisely and neatly. For example, the specific behavior constraints for \emph{Sync} channel are classified into two types: data constraints and time constraints. The description and the definition of \emph{Sync} in Coq have already clearly expressed the behavior pattern it needs to follow: each item in data and time streams of output specified as ``node[1]'' is equivalent to the timed data items of input specified as ``node[0]'', which are exactly data and time constraints. As they are both requirements that we need to satisfy no matter data or time is related, each constraint in the list will all be merged finally.
\lstset{language=Python}
\begin{lstlisting}[frame=single]
def Sync(nodes, bound):
   assert len(nodes) == 2
   constraints = []
   for i in range(bound):
     constraints += [ nodes[0]['data'][i] == nodes[1]['data'][i] ]
     constraints += [ nodes[0]['time'][i] == nodes[1]['time'][i] ]
   return Merge(constraints)
\end{lstlisting}

\emph{Syncdrain} and \emph{FIFO1} channel are defined in a similar way. On the basis of the behavior of \emph{Syncdrain} channel, there are only time related constraints to be needed, i.e., equivalence of each item in two time streams of the two inputs. Regarding \emph{FIFO1} channels, constraints related data is the same as \emph{Sync} channels. But there are more time related constraints. As the buffer capacity is one, the relation of each item in the input time stream and output time stream need to be carefully dealt with, especially that the next input should be later than the output at present. At last, their corresponding constraint lists consist of constraint statements similar to the statements above.
\begin{lstlisting}[frame=single]
def SyncDrain(nodes, bound):
   assert len(nodes) == 2
   constraints = []
   for i in range(bound):
       constraints +=
            [nodes[0]['time'][i] == nodes[1]['time'][i]]
   return Merge(constraints)
\end{lstlisting}
\begin{lstlisting}[frame=single]
def Fifo1(nodes, bound):
   assert len(nodes) == 2
   constraints = []
   for i in range(bound):
      constraints +=
                  [ nodes[0]['data'][i] == nodes[1]['data'][i] ]
      constraints +=
                  [ nodes[0]['time'][i] <  nodes[1]['time'][i] ]
      if i:
          constraints +=
                  [ nodes[0]['time'][i] > nodes[1]['time'][i-1] ]

   return Merge(constraints)
\end{lstlisting}

In accordance with the behavior of \emph{Lossy} channel, each item of the input stream may or may not be lost. If so, then the output gets nothing. If not, it behaves exactly like \emph{Sync} channel, so in this case the data and time related constraints are identical with those in the definition of \emph{Sync} channel. The biggest difference is that \emph{Lossy} channel should be defined in a recursive way according to its own distinctive behavior. Note that the constraints are added in a recursive way which is in great coincidence with the original definition.
\begin{lstlisting}[frame=single]
def Lossy(nodes, bound, idx = 0, num = 0):
   assert len(nodes) == 2
   if bound == num:
     return True
   if bound == idx:
     return True
   constraints_0 = []
   constraints_1 = []
   constraints_0 +=
           [ nodes[0]['data'][idx] != nodes[1]['data'][num]]
   constraints_0 +=
           [ nodes[0]['time'][idx] != nodes[1]['time'][num]]
   constraints_1 +=
           [ nodes[0]['data'][idx] == nodes[1]['data'][num]]
   constraints_1 +=
           [ nodes[0]['time'][idx] == nodes[1]['time'][num]]
   return Or(And(Merge(constraints_0),
             Channel.Lossy(nodes, bound, idx + 1, num)),
             And(Merge(constraints_1),
             Channel.Lossy(nodes, bound, idx + 1, num + 1))
             )
\end{lstlisting}
\subsection{Composition Operators}
While the basic channels are already well defined as the basis of the whole construction framework, the composition operators also need to be specified for the large-scale connector construction just like cement for bricks.

Among the three types of composition operators, the most important and difficult one is \emph{Merge}, which is specially dealt with as a channel \emph{Merger} in our model. Although the composition operator \emph{Merge} is treated as a channel \emph{Merger}, it also play the same part in the construction of a connector.  Plus the rest of composition operators: \emph{replicate} and \emph{flow-through}, they are enough for the whole construction for any connector, which can serve as same as the original composition operations. For each item of output stream, there is a nondeterministic choice between the two input nodes. Hence, the \emph{Merger} channel also need to be defined in a recursive way like \emph{Lossy} channel. Note that the constraints also conform well to the original definition of \emph{Merge}. Concluded from the two recursive definitions, an additional advantage of defining \emph{Lossy} and \emph{Merger} channel in this way is that it can preserve the behavioral pattern to a great extent without many assumptions such as priorities of reading or taking data.
\begin{lstlisting}[frame=single]
def Merger(nodes, bound, idx_1 = 0, idx_2 = 0):
   assert len(nodes) == 3
   if bound == idx_1 + idx_2:
     return True
   constraints_1 = []
   constraints_2 = []
   constraints_1 +=
    [ nodes[0]['data'][idx_1] == nodes[2]['data'][idx_1 + idx_2]]
   constraints_1 +=
    [ nodes[0]['time'][idx_1] == nodes[2]['time'][idx_1 + idx_2]]
   constraints_1 +=
    [ nodes[0]['time'][idx_1] <  nodes[1]['time'][idx_2]]
   constraints_2 +=
    [ nodes[1]['data'][idx_2] == nodes[2]['data'][idx_1 + idx_2]]
   constraints_2 +=
    [ nodes[1]['time'][idx_2] == nodes[2]['time'][idx_1 + idx_2]]
   constraints_2 +=
    [ nodes[1]['time'][idx_2] <  nodes[0]['time'][idx_1]]
   return Or(And(Merge(constraints_1),
             Channel.Merger(nodes, bound, idx_1 + 1, idx_2)),
             And(Merge(constraints_2),
             Channel.Merger(nodes, bound, idx_1, idx_2 + 1))
             )
\end{lstlisting}
\emph{Replicate} and \emph{flow-through} operators are implicitly achieved when we compose channels to construct connectors using the same node names. A simple example for the implementation of \emph{replicate} is \emph{c1.connect(`Sync', `A', `E'), c1.connect(`Fifo1', `E', `F'), c1.connect(`Fifo1', `E', `G')} where message from node `E' is copied to send to nodes `F' and `G' simultaneously. As for \emph{flow-through} operator, a simple example is \emph{c2.connect(`Fifo1', `A', `D'), c2.connect(`Sync', `D', `B')} where the timed data flows from node `A' to node `B' through the mixed node `D'. In these two simple examples, \emph{c1} and \emph{c2} both belong to connector class which will be elaborated in detail in next module.
\subsection{Reasoning about refinement relation}
With basic channels and composition operators well formulated above, we are left with the task of first constructing Reo connectors. In this model, connector is defined as a new class, which provides a method of constructing complex connectors out of channels and operators.
The statements inside a class definition are function definitions. We have seen the function `connect' used in the two simple examples of \emph{replicate} and \emph{flow-through}.
\begin{lstlisting}[frame=single]
class Connector:
    def __init__(self):
        self.channels = []

@@

The soundness of the function \textbf{\emph{isRefinementOf}} is presented as a theorem as follows.

The formal definition of \textbf{\emph{isRefinementOf}} is given as an algorithm here, with the details left out.
\begin{algorithm}[t]
    \caption{\ \ Q.isRefinementOf (P, bound)}
    \begin{algorithmic}[1]
        \REQUIRE Both P and Q are connector.
        \ENSURE A boolean: \emph{True} or \emph{False with a counterexample}
        \FOR{channel \emph{t} $\leftarrow$ \emph{Q}}
        	\FOR{node \emph{n} $\leftarrow$ \emph{t}}
				\IF{\emph{n} is a new node}
					\STATE \emph{\large i.}generate the corresponding variable like 					
						\newline  \{`time':[n\_t\_0, n\_t\_1,...,n\_t\_(bound-1)],\  `date':[n\_d\_0, n\_d\_1,...,n\_d\_(bound-1)]\}
						\newline
						\newline \emph{\large ii.}add time constraints like ``n\_t\_0 $\geq$ 0  and  n\_t\_i $<$ n\_t\_i+1'' into \emph{Solver()}
				\ENDIF
			\ENDFOR
		\STATE Add the constraints between different nodes of the same channel into \emph{Solver()} according to the property of channels.
        \ENDFOR
        \newline
        \STATE foralls = []      %\% to store new variable
        \STATE absGlobalConstr = None %\% to store all constraints under P
        \STATE absTimeConstr = None %\% to store all timed constraints under P
        \FOR{channel \emph{t} $\leftarrow$ \emph{P}}
        	\FOR{node \emph{n} $\leftarrow$ \emph{t}}
				\IF{\emph{n} is a new node}
					\STATE \emph{\large i.}generate the corresponding variable like 					
						\newline \{`time':[n\_t\_0, n\_t\_1,...,n\_t\_(bound-1)], `date':[n\_d\_0, n\_d\_1,...,n\_d\_(bound-1)]\}
						\newline
						\newline \emph{\large ii.}add \emph{n} into forall
						\newline
						\newline \emph{\large iii.}add time constraints like ``n\_t\_0 $\geq$ 0  and  n\_t\_i $<$ n\_t\_i+1'' into absTimeConstr
				\ENDIF
			\STATE add the constraints between different nodes of the same channel into absGlobalConstr according to the property of channels.
			\ENDFOR
		\ENDFOR
		\newline
	\IF{absTimeConstr is not None}
		\STATE $absGlobalConstr = \neg \ (absTimeConstr \cap absGlobalConstr)  $
	\ELSE
		\STATE $absGlobalConstr = \neg \ absGlobalConstr$
	\ENDIF
	\IF{forall is not empty}
		\STATE apply \emph{ForAll} to absGlobalConstr
			 and add those constraints into \emph{Solver()}
    \ELSE
    	\STATE add absGlobalConstr into \emph{Solver()}
	\ENDIF	
    \STATE \emph{Solver.check()}.
    \end{algorithmic}
\end{algorithm}

@@

\end{example}
The following large-scale example is aimed at complementary refinement checking.
\subsection{Z3 vs Coq}
Having seen the examples proved by Coq or Z3 solver, we can summarize their features and make a comparison between them.
In the preceding proof about refinement relation or other properties in Coq, the main feature is that users need to master the tactics and strategies well to give a proof of the properties. But there is no need to worry the time consumed in the proof. It will be efficient no matter how large the connectors are as long as users have choose proper tactics. Besides, the connectors whose properties have been proved can be regarded as a theorem when proving properties of much larger ones. Recall that the reason of introducing Z3 solver is that complementary refinement checking, i.e., one connector is not  a refinement of the other one, can't be provided by Coq, let alone provide counterexamples or witnesses.

>>>>

\subsection{The Coordination Model Reo}
Reo is a channel-based exogenous coordination model wherein complex coordinators, called connectors,
are compositionally built out of simpler ones \cite{Arb04}.
Further details about Reo and its semantics can be found in \cite{Arb04,AR03,BSAR06}.
The simplest connectors are channels with well-defined behavior such as synchronous channels, FIFO channels, etc.
Each channel in Reo has exactly two directed ends, with their own identities.
There are two types of channel ends: source ends and sink ends. A source channel end accepts
data into the channel. A sink channel end dispenses data out of the channel.
\begin{figure}
  \centering
  \begin{tikzpicture}
  \draw (0.7, 0.6) node[draw=none] {Sync};
  \sync{(0,1)}{(1.5,1)}{}
  \draw (2.7, 0.6) node[draw=none] {Syncdrain};
  \syncdrain{(2,1)}{(3.5,1)}{node[below]{}}
  \draw (4.7, 0.6) node[draw=none] {FIFO1};
  \fifoe{(4,1)}{(5.5,1)}{node[below]{}}
  \draw (8.7, 0.6) node[draw=none] {LossySync};
  \lossysync{(8,1)}{(9.5,1)}{node[below left]{}}
  \end{tikzpicture}\vspace{-6mm}
  \caption{Four types of basic channels.}\label{fig:basicchannel}
\end{figure}

@@

By means of function \emph{Conjunction}, basic channels are defined concisely and neatly. For example, the specific behavior constraints for \emph{Sync} channel are classified into two types: data constraints and time constraints. The description and the definition of \emph{Sync} in Coq have already clearly expressed the behavior pattern it needs to follow: each item in data and time streams of output specified as ``node[1]'' is equivalent to the timed data items of input specified as ``node[0]'', which are exactly data and time constraints. As they are both requirements that we need to satisfy no matter data or time is related, each constraint in the list will all be merged finally.
%\lstset{language=Python}
\begin{lstlisting}[frame=single]
def Sync(nodes, bound):
   assert len(nodes) == 2
   constraints = []
   for i in range(bound):
     constraints +=
        [ nodes[0]['data'][i] == nodes[1]['data'][i] ]
     constraints +=
        [ nodes[0]['time'][i] == nodes[1]['time'][i] ]
   return Conjunction(constraints)
\end{lstlisting}

\emph{Syncdrain} channel are defined in a similar way. On the basis of the behavior of \emph{Syncdrain} channel, there are only time related constraints to be needed, i.e., equivalence of each item in two time streams of the two inputs.
\begin{lstlisting}[frame=single]
def SyncDrain(nodes, bound):
   assert len(nodes) == 2
   constraints = []
   for i in range(bound):
       constraints +=
            [nodes[0]['time'][i] == nodes[1]['time'][i]]
   return Conjunction(constraints)
\end{lstlisting}
Regarding \emph{FIFO1} channels, constraints related data is the same as \emph{Sync} channels. But there are more time related constraints. As the buffer capacity is one, the relation of each item in the input time stream and output time stream need to be carefully dealt with, especially that the next input should be later than the output at present. If the buffer contains a data item at first, i.e. the variant version \emph{FIFO1e} channel, then the constraints related to data and time are just a little different. Note that the data item ``\emph{e}'' in the buffer should be the first for transit and all the differences made to the constraints result from it. At last, their corresponding constraint lists consist of constraint statements similar to the statements above.
\begin{lstlisting}[frame=single]
def Fifo1(nodes, bound):
   assert len(nodes) == 2
   constraints = []
   for i in range(bound):
      constraints +=
                  [ nodes[0]['data'][i] == nodes[1]['data'][i] ]
      constraints +=
                  [ nodes[0]['time'][i] <  nodes[1]['time'][i] ]
      if i:
          constraints +=
                  [ nodes[0]['time'][i] > nodes[1]['time'][i-1] ]
   return Conjunction(constraints)
\end{lstlisting}
\begin{lstlisting}[frame=single]
def Fifo1e(nodes, bound):
   assert len(nodes) == 2
   constraints = []
   constraints += [nodes[1]['data'][0] == 1]
   for i in range(bound-1):
      constraints +=
                  [nodes[0]['data'][i] == nodes[1]['data'][i + 1]]
      constraints +=
                  [nodes[0]['time'][i] < nodes[1]['time'][i + 1]]
   for i in range(bound):
      constraints +=
                  [nodes[0]['time'][i] > nodes[1]['time'][i]]
   return Merge(constraints)
\end{lstlisting}

In accordance with the behavior of \emph{Lossy} channel, each item of the input stream may or may not be lost. If so, then the output gets nothing. If not, it behaves exactly like \emph{Sync} channel, so in this case the data and time related constraints are identical with those in the definition of \emph{Sync} channel. The biggest difference is that \emph{Lossy} channel should be defined in a recursive way according to its own distinctive behavior. Note that the constraints are added in a recursive way which is in great coincidence with the original definition.
\begin{lstlisting}[frame=single]
def Lossy(nodes, bound, idx = 0, num = 0):
   assert len(nodes) == 2
   if bound == num:
     return True
   if bound == idx:
     return True
   constraints_0 = []
   constraints_1 = []
   constraints_0 +=
           [ nodes[0]['data'][idx] != nodes[1]['data'][num]]
   constraints_0 +=
           [ nodes[0]['time'][idx] != nodes[1]['time'][num]]
   constraints_1 +=
           [ nodes[0]['data'][idx] == nodes[1]['data'][num]]
   constraints_1 +=
           [ nodes[0]['time'][idx] == nodes[1]['time'][num]]
   return Or(And(Conjuction(constraints_0),
             Channel.Lossy(nodes, bound, idx + 1, num)),
             And(Conjunction(constraints_1),
             Channel.Lossy(nodes, bound, idx + 1, num + 1))
             )
\end{lstlisting}
\subsection{Composition Operators}
While the basic channels are already well defined as the basis of the whole construction framework, the composition operators also need to be specified for the large-scale connector construction just like cement for bricks.

Among the three types of composition operators, the most important and difficult one is \emph{Merge}, which is specially dealt with as a channel \emph{Merger} in our model. Although the composition operator \emph{Merge} is treated as a channel \emph{Merger}, it also plays the same part in the construction of a connector.  Plus the rest of composition operators: \emph{replicate} and \emph{flow-through}, they are enough for the whole construction for any connector, which can serve as same as the original composition operations. For each item of output stream, there is a nondeterministic choice between the two input nodes. Hence, the \emph{Merger} channel also need to be defined in a recursive way like \emph{Lossy} channel. Note that the constraints also conform well to the original definition of \emph{Merge}. Concluded from the two recursive definitions, an additional advantage of defining \emph{Lossy} and \emph{Merger} channel in this way is that it can preserve the behavioral pattern to a great extent without many assumptions such as priorities of reading or taking data.
\begin{lstlisting}[frame=single]
def Merger(nodes, bound, idx_1 = 0, idx_2 = 0):
   assert len(nodes) == 3
   if bound == idx_1 + idx_2:
     return True
   constraints_1 = []
   constraints_2 = []
   constraints_1 +=
    [ nodes[0]['data'][idx_1] == nodes[2]['data'][idx_1 + idx_2]]
   constraints_1 +=
    [ nodes[0]['time'][idx_1] == nodes[2]['time'][idx_1 + idx_2]]
   constraints_1 +=
    [ nodes[0]['time'][idx_1] <  nodes[1]['time'][idx_2]]
   constraints_2 +=
    [ nodes[1]['data'][idx_2] == nodes[2]['data'][idx_1 + idx_2]]
   constraints_2 +=
    [ nodes[1]['time'][idx_2] == nodes[2]['time'][idx_1 + idx_2]]
   constraints_2 +=
    [ nodes[1]['time'][idx_2] <  nodes[0]['time'][idx_1]]
   return Or(And(Merge(constraints_1),
             Channel.Merger(nodes, bound, idx_1 + 1, idx_2)),
             And(Merge(constraints_2),
             Channel.Merger(nodes, bound, idx_1, idx_2 + 1))
             )
\end{lstlisting}
\emph{Replicate} and \emph{flow-through} operators are implicitly achieved when we compose channels to construct connectors using the same node names. A simple example for the implementation of \emph{replicate} is \emph{c1.connect(`Sync', `A', `E'), c1.connect(`Fifo1', `E', `F'), c1.connect(`Fifo1', `E', `G')} where message from node `E' is copied to send to nodes `F' and `G' simultaneously. As for \emph{flow-through} operator, a simple example is \emph{c2.connect(`Fifo1', `A', `D'), c2.connect(`Sync', `D', `B')} where the timed data flows from node `A' to node `B' through the mixed node `D'. In these two simple examples, \emph{c1} and \emph{c2} both belong to connector class which will be elaborated in detail in next module.
\subsection{Reasoning about refinement relation}
With basic channels and composition operators well formulated above, we are left with the task of first constructing Reo connectors. In this model, connector is defined as a new class, which provides a method of constructing complex connectors out of channels and operators.
The statements inside a class definition are function definitions. We have seen the function `connect' used in the two simple examples of \emph{replicate} and \emph{flow-through}.
\begin{lstlisting}[frame=single]
class Connector:
    def __init__(self):
        self.channels = []

@@

The soundness of the function \textbf{\emph{isRefinementOf}} is presented as a theorem as follows.
\begin{theorem}[Soundness Theorem]
The algorithm won't produce fake counter-examples.
\end{theorem}

\begin{proof}
Assume the bound we set is \emph{b}. For any channel, the constraints used in Z3 is bounded, i.e., only part of the constraints of timed data stream are fed to Z3. Let the set of all constraints of connectors considered be $\Sigma$ and the constraints of bounded ones be $\sigma$. We have $\sigma \sqsubset \Sigma$. If there exists a counterexample $\pi$ and the weaker constraints can't be satisfied: $\pi \nvDash \sigma$, then we can deduce that $\pi \nvDash \Sigma$. Let $\Pi$ be the full timed data stream where $\pi$ is the prefix of it and $\Pi \setminus \pi$ satisfies all the left constraints $\Sigma \setminus \sigma$.
A valid prefix leads to a valid timed data stream, hence we have $\Pi \nvDash \sigma$.
The counterexamples are always true.
\end{proof}
The formal definition of \textbf{\emph{isRefinementOf}} is given as an algorithm here, with the details left out.
\begin{algorithm}[t]
    \caption{\ \ Q.isRefinementOf (P, bound)}
    \begin{algorithmic}[1]
        \REQUIRE Both P and Q are connector.
        \ENSURE A boolean: \emph{True} or \emph{False with a counterexample}
        \FOR{channel \emph{t} $\leftarrow$ \emph{Q}}
        	\FOR{node \emph{n} $\leftarrow$ \emph{t}}
				\IF{\emph{n} is a new node}
					\STATE \emph{\large i.}generate the corresponding variable like 					
						\newline  \{`time':[n\_t\_0, n\_t\_1,...,n\_t\_(bound-1)],\  `date':[n\_d\_0, n\_d\_1,...,n\_d\_(bound-1)]\}
						\newline
						\newline \emph{\large ii.}add time constraints like ``n\_t\_0 $\geq$ 0  and  n\_t\_i $<$ n\_t\_i+1'' into \emph{Solver()}
				\ENDIF
			\ENDFOR
		\STATE Add the constraints between different nodes of the same channel into \emph{Solver()} according to the property of channels.
        \ENDFOR
        \newline
        \STATE foralls = []      %\% to store new variable
        \STATE absGlobalConstr = None %\% to store all constraints under P
        \STATE absTimeConstr = None %\% to store all timed constraints under P
        \FOR{channel \emph{t} $\leftarrow$ \emph{P}}
        	\FOR{node \emph{n} $\leftarrow$ \emph{t}}
				\IF{\emph{n} is a new node}
					\STATE \emph{\large i.}generate the corresponding variable like 					
						\newline \{`time':[n\_t\_0, n\_t\_1,...,n\_t\_(bound-1)], `date':[n\_d\_0, n\_d\_1,...,n\_d\_(bound-1)]\}
						\newline
						\newline \emph{\large ii.}add \emph{n} into forall
						\newline
						\newline \emph{\large iii.}add time constraints like ``n\_t\_0 $\geq$ 0  and  n\_t\_i $<$ n\_t\_i+1'' into absTimeConstr
				\ENDIF
			\STATE add the constraints between different nodes of the same channel into absGlobalConstr according to the property of channels.
			\ENDFOR
		\ENDFOR
		\newline
	\IF{absTimeConstr is not None}
		\STATE $absGlobalConstr = \neg \ (absTimeConstr \cap absGlobalConstr)  $
	\ELSE
		\STATE $absGlobalConstr = \neg \ absGlobalConstr$
	\ENDIF
	\IF{forall is not empty}
		\STATE apply \emph{ForAll} to absGlobalConstr
			 and add those constraints into \emph{Solver()}
    \ELSE
    	\STATE add absGlobalConstr into \emph{Solver()}
	\ENDIF	
    \STATE \emph{Solver.check()}.
    \end{algorithmic}
\end{algorithm}

@@

\begin{example}
Fig.\ref{fig:large} shows an example of the application of a two-node sequencer, with the addition of a pair of \emph{Sync} channels and a \emph{SyncDrain} channel connecting each of the nodes of the sequencer to the nodes
\emph{A} and \emph{C}, and \emph{B} and \emph{C}, respectively. The leftmost channel is initialized to have a data item in its buffer, as indicated
by the presence of the symbol \emph{e} in the box, which is actually a \emph{FIFO1e} channel. As the sequencer ensures that the take operation on nodes \emph{G} and \emph{H} can succeed only in the strict left-to-right order, the behavior of the connector can be seen as imposing an order on the flow of the data items written to \emph{A} and \emph{B}. The timed data stream obtained by successive take operations on \emph{C} consists of the first data item written to \emph{B}, followed by the first data item written to \emph{A}, followed by the second data item written to \emph{B}, and so on. The variant connector is obtained by replacing the pair of \emph{Sync} channels with a pair of \emph{Sync} channel and \emph{Lossy} channel. On account of the behavior of \emph{Lossy} channel, the first data item written to \emph{B} can be lost, which leads to the failure of the sequence order. Thus, the variant connector is not a refinement of the original connector, but the original connector is indeed a refinement of the variant connector. The details of the concrete construction and counterexample are left out. The results Z3 solver presented are \emph{False} for \emph{c2.isRefinementOf(c1)} and \emph{True} for \emph{c1.isRefinementOf(c2)}, which are consistent with the theoretical deduction.
\begin{figure}
\centering
\begin{tikzpicture}
	\node (note1) at (5.1, -2.6) {\small (a) Sequencer};
    \node (note2) at (11.5, -2.6) {\small (b) Variant Sequencer};
    \node (note3) at (4.25,-1.1) {e};
    \node (note3) at (10.75,-1.1) {e};

    \ionode{(inup)}{(3.5, 0.8)}{node[left] {A}}
    \ionode{(indown)}{(3.5, 0)}{node[left] {B}}
    \ionode{(out)}{(7.7,0.8)}{node[right] {C}}
    \mixednode{(mid1up)}{(6.5, 0.8)}{node[above] {D}}
    \mixednode{(mid1down)}{(5, 0)}{node[above] {E}}
    \mixednode{(mid2left)}{(3.5, -1.1)}{node[left] {F}}
    \mixednode{(mid2mid)}{(5, -1.1)}{node[below] {G}}
    \mixednode{(mid2right)}{(6.5, -1.1)}{node[right] {H}}
    \sync{(inup)}{(mid1up)}{}
    \sync{(mid1up)}{(out)}{}
    \sync{(indown)}{(mid1down)}{}
    \draw [-](5,0) -- (6.8,0)node[below]{};
    \draw [->](6.8,0) -- (7.6,0.7)node[below]{};
    \syncdrain{(mid1down)}{(mid2mid)}{}
    \syncdrain{(mid1up)}{(mid2right)}{}
    \fifoe{(mid2left)}{(mid2mid)}{}
    \fifoe{(mid2mid)}{(mid2right)}{}
    \draw [-](6.5,-1.1) -- (6.5,-1.8)node[below]{};
    \draw [-](6.5,-1.8) -- (3.5,-1.8)node[below]{};
    \draw [->](3.5,-1.8) -- (3.5,-1.2)node[below]{};

    \ionode{(pinup)}{(10, 0.8)}{node[left] {A}}
    \ionode{(pindown)}{(10, 0)}{node[left] {B}}
    \ionode{(pout)}{(14.2,0.8)}{node[right] {C}}
    \mixednode{(pmid1up)}{(13, 0.8)}{node[above] {D}}
    \mixednode{(pmid1down)}{(11.5, 0)}{node[above] {E}}
    \mixednode{(pmid2left)}{(10, -1.1)}{node[left] {F}}
    \mixednode{(pmid2mid)}{(11.5, -1.1)}{node[below] {G}}
    \mixednode{(pmid2right)}{(13, -1.1)}{node[right] {H}}
    \sync{(pinup)}{(pmid1up)}{}
    \lossysync{(pmid1up)}{(pout)}{}
    \sync{(pindown)}{(pmid1down)}{}
    \draw [dashed](11.5,0) -- (13.3,0)node[below]{};
    \draw [dashed](13.3,0) -- (14,0.7)node[below]{};
    \draw [->](13.9,0.6) -- (14,0.7)node[below]{};
    \syncdrain{(pmid1down)}{(pmid2mid)}{}
    \syncdrain{(pmid1up)}{(pmid2right)}{}
    \fifoe{(pmid2left)}{(pmid2mid)}{}
    \fifoe{(pmid2mid)}{(pmid2right)}{}
    \draw [-](13,-1.1) -- (13,-1.8)node[below]{};
    \draw [-](13,-1.8) -- (10,-1.8)node[below]{};
    \draw [->](10,-1.8) -- (10,-1.2)node[below]{};
    \end{tikzpicture}
\caption{Example of connector complementary refinement }
\label{fig:large}
\end{figure}
\end{example}
\subsection{Z3 vs Coq}
Having seen the examples proved by Coq or Z3 solver, we can summarize their features and make a comparison between them.
In the preceding proof about refinement relation or other properties in Coq, the main feature is that users need to master the tactics and strategies well to give a proof of the properties. But there is no need to worry the time consumed in the proof. It will be efficient no matter how large the connectors are as long as users have choose proper tactics. Besides, the connectors whose properties have been proved can be regarded as a theorem when proving properties of much larger ones. Recall that the reason of introducing Z3 solver is that complementary refinement checking, i.e., one connector is not  a refinement of the other one, can't be provided by Coq, let alone provide counterexamples or witnesses.
